Blockchain System

### 2020-08-25 papers/execution-model/model.tex
partial update

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\newtheorem{mydef}{Definition}
\newtheorem{mylemma}{Lemma}
\newtheorem{mytheorem}{Theorem}
\newtheorem{mypro}{Proposition}

@@

\end{definition}
 \begin{definition}[State of a node]
   The state of a node is a tuple
   $[\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

@@

\begin{definition}[Blockchain system]
A blockchain system is a pair
$\langle \mathbf{M}, \mathbf{B} \rangle$ where
\begin{enumerate}
\item $\mathbf{M} = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\mathbf{B} = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
\end{enumerate}
\end{definition}

\section{Rules}
\subsection{Transfers}

@@

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
\text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

@@

\begin{equation}
\frac{}{
  \begin{array}{l}
    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \rightarrow \\
    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
  s)$, $\TIME' + 1$]}
  \end{array}
}\label{eq:1}
\end{equation}
~\\
Rule 8 [timeout]:
\begin{equation}{}
\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[transfer $n$ from $puk$ to  $puh$ fee $m$, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
\text{[\PENDING, \ACCEPTED, updatecou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

>>>>

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}

@@

\end{definition}
 \begin{definition}[State of a node]
   The state of a node is a tuple
   $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ where $\ACCOUNTS$ is a set of accounts,
   $\OPERATIONS$ a set of operations, and $\CONTRACTS$  a set of contracts. 
\end{definition}

@@

\begin{definition}[Blockchain system]
A blockchain system is a pair
$ \NODE \| \BLOCKCHAIN$ where
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
\end{enumerate}
\end{definition}

\section{Rules}

\subsection{Transitions on Nodes}
\label{sec:transitions-nodes}

Each node has (nondeterministic) rules to propose an operation.

\begin{mathpar}
  \inferrule[Node-Transfer]
  {\CHECKACC (\PUK, \ACCOUNTS)
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans
    [\ACCOUNTS, (\TRANSFER\NTEZ\PUK{\PUK'}\MTEZ) :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-Originate]
  {\CHECKACC (\PUK, \ACCOUNTS) \\
    \CHECKID (\ID, \CONTRACTS)
  }{
    [\ACCOUNTS, \OPERATIONS, \CONTRACTS]
    \NodeTrans \\
    [\ACCOUNTS, (\ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ) :: \OPERATIONS, \CONTRACTS]
  }

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE \| \BLOCKCHAIN} \SystemTrans {\NODE'\| \BLOCKCHAIN}}
\end{mathpar}

\subsection{Transfers}

@@

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\\\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS, \CONTRACTS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS, \CONTRACTS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$}\\
% \text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [($<$ transfer $n$ from $puk$ to $puk'$ fee $m$, generateOph($pkh$, }\\
% \text{$pkh', n, m$, \TIME), \TIME $>$) :: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of counter]:

@@

\begin{equation}{}
  \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
  {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
        [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
        \rightarrow \langle$[\ACCOUNTS, 
        (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

@@

\begin{equation}
\frac{}{
  \begin{array}{l}
    {[\langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME
    \rangle :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']}
    \rightarrow \\
    {}[\PENDING, \langle \TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \OPH, \TIME' \rangle :: \ACCEPTED,  \\
    \text{updateSucc(\MANAGERS, \PUK, '', \NTEZ, \MTEZ), updateConstr$(\CONTRACTORS, \PUH, \NTEZ,
  s)$, $\TIME' + 1$]}
  \end{array}
}\label{eq:1}
\end{equation}
~\\
Rule 8 [timeout]:
\begin{equation}{}
  \frac{\TIME' - \TIME \ge 60}{
    \begin{array}{l}
      {}[\langle\TRANSFER[\STRING]\NTEZ\PUK\PUH\MTEZ, \TIME\rangle ::
      \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ]
      \rightarrow \\
      {}[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE), \CONTRACTORS, \TIME']
    \end{array}
    }
\end{equation}
